Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-27 Paper.tex
Minor corrections

\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\section{Introduction}\label{sec:introduction}

@@

\begin{itemize}
\item Is the most used and mature
Turing-complete-programmable blockchain technology.
\item Support for high quality and audited
libraries in Solidity (most used smart contract language in Ethereum).
\item Developments on Ethereum can be deployed
over public (main or test-nets) or private/permissioned networks.
\item Unlike Bitcoin, Ethereum supports miner fees using gas
instead of directly ETH; this can mitigate the effects of
volatile crypto-currency price by adjusting gas price depending
on ETH value.
\end{itemize}

@@

On execution uses the module \texttt{lib/iptables.js}
to setup and initialize system's iptables redirecting
all 80 port traffic to the ip address of Raspberry's
ip address; to do so, relies on the node module \texttt{child\_process}
to spawn system commands. Also redirects all traffic trying
to reach 8545 port to itself the same way in order to
redirect MetaMask's RCP calls to the lightweight infuraProxy\cite{infuraProxy}
developed also for this project and contained in etherwall's root directory.

@@

Blockchains, specially public ones are subject of several controversy
regarding regulation compliance; regulations like GDPR for data protection
and privacy and eIDAS regarding digital signature present some friction
at some aspects of blockchain based solutions; also, there's the
smart contract figure regarding how can it be legally binding
in order to ensure solutions built
for the project are 100\% European regulation compliant;
it's recommended to study implications but not
defining the kind of Ethereum blockchain (permissioned, private or public)
until having a clear guarantee that all features supported are legally
feasible on a final chosen deployment environment.

>>>>

\newpage
\setlength{\columnsep}{20pt}
\begin{multicols}{2}
\section{Introduction}\label{sec:introduction}

@@

\begin{itemize}
\item Is the most used and mature
Turing-complete-programmable blockchain technology.
\item Supports high quality and audited
libraries in Solidity (most used smart contract language in Ethereum).
\item Developments on Ethereum can be deployed
over public (main or test-nets) or private/permissioned networks.
\item Unlike Bitcoin, Ethereum supports miner fees using gas
instead of directly ETH; this can mitigate the effects of
volatile crypto-currency price by adjusting gas price depending
on ETH value.
\end{itemize}

@@

On execution uses the module \texttt{lib/iptables.js}
to setup and initialize system's iptables redirecting
all 80 port traffic to Raspberry's
ip address; to do so, relies on the node module \texttt{child\_process}
to spawn system commands. Also redirects all traffic trying
to reach 8545 port to itself the same way in order to
redirect MetaMask's RCP calls to the lightweight infuraProxy\cite{infuraProxy}
developed also for this project and contained in etherwall's root directory.

@@

Blockchains, specially public ones are subject of several controversy
regarding regulation compliance; regulations like GDPR for data protection
and privacy and eIDAS regarding digital signature present some friction
at some aspects of blockchain based solutions; also, there's the
smart contract figure regarding how can it be legally binding
in order to ensure solutions built
for the project are 100\% European regulation compliant;
it's recommended to study implications
until having a clear guarantee that all features supported are legally
feasible on a final chosen deployment environment.
